251 MA

### 2023-01-18 code/process.Rmd
getting closer!

d |> filter(!status %in% c("missing", "non-experiment", "reproduction", "TODO")) |> tally()
```
We have maybe as many as 178 at least for some analyses.

@@

- "great" means we have all relevant cells coded in spreadsheet

- "ES_direction" is great except that we don't have the direction coded (ex. is an interaction that I can't eyeball, or a multi-way F test with no graph)

- "stuck" means that I'm stuck somewhere -- we don't have everything filled in, but it may be possible to get there

- "hopeless" means we don't have everything filled in, but I don't believe filling in more/all is possible

- "TODO" means I'm still working on data coding (this year's projects)

@@

```{r}
parse_beta_ci <- function(raw_stat){
  beta=str_extract(raw_stat, "b=.*\\[") |> str_sub(3,-2) |> as.numeric()
  low=str_extract(raw_stat, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high=str_extract(raw_stat, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  se=high-low/(2*1.96)
  zval=beta/se
    pval=2*pnorm(zval, lower.tail=F)
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "beta"=beta, "SE"=se))
}

@@

do_blanks <- function(){
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "beta"=NA, "SE"=NA))
}
do_parsing=function(raw_stat, within_between,n){
  if (is.na(raw_stat)) {return (do_blanks())}
  if (str_sub(raw_stat,1,1)=="t"){return(parse_t(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="F"){return(parse_f(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="c"){return(parse_chisq(raw_stat, within_between))}
  if (str_sub(raw_stat, 1,3)=="MCI"){return(parse_mean_ci(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSD"){return(parse_mean_sd(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSE"){return(parse_mean_se(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,8)=="wilcoxon"){return(parse_wilcoxon(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bse"){return(parse_beta_se(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bci"){return(parse_beta_se(raw_stat))}

@@

d_check_nas |> filter(across(everything(), ~!is.na(.))) |> nrow()

@@

d_check_nas |> select(target_lastauthor_year, status, academic_year, subfield, target_year,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N,
           sub_rep) |> filter(across(everything(), ~!is.na(.))) |> nrow()

@@

d_check_nas |> select(target_lastauthor_year, status, academic_year, subfield, target_year,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N, predInt, p_orig,
           sub_rep) |>  filter(across(everything(), ~!is.na(.))) |> nrow()
```

>>>>

d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> tally()
```
We have maybe as many as 177 at least for some analyses.

@@

- "complete" -- it's a full case

- "adj" -- will be a full case once we get subjective replication and subfield coded

- "beta" -- don't have standardized ES, but have a pair that we can do predInt to

- "ES_direction" -- we don't have the direction coded (ex. is an interaction that I can't eyeball, or a multi-way F test with no graph)

- "ask" -- might be salvageable, but I have questions about coding

- "done" -- got as far as I can, and that is that we have demographics but not stats

- "unusable" -- got as far as I can, and it does not have complete descriptives

- "missing" -- student didn't finish or we don't have write-up

- "non-experiment" -- student replicated something that was not an experiment

- "reproduction" -- student did a reproduction and not replication

@@

parse_beta_ci <- function(raw_stat){
  beta=str_extract(raw_stat, "b=.*\\[") |> str_sub(3,-2) |> as.numeric()
  low=str_extract(raw_stat, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high=str_extract(raw_stat, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  se=high-low/(2*1.96)
  zval=beta/se
    pval=2*pnorm(zval, lower.tail=F)
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "beta"=beta, "SE"=se))
}

@@

do_blanks <- function(){
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "beta"=NA, "SE"=NA))
}
do_parsing=function(raw_stat, within_between,n){
  if (is.na(raw_stat)) {return (do_blanks())}
  if (str_sub(raw_stat,1,1)=="t"){return(parse_t(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="F"){return(parse_f(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="c"){return(parse_chisq(raw_stat, within_between))}
  if (str_sub(raw_stat, 1,3)=="MCI"){return(parse_mean_ci(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSD"){return(parse_mean_sd(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSE"){return(parse_mean_se(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,8)=="wilcoxon"){return(parse_wilcoxon(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bse"){return(parse_beta_se(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bci"){return(parse_beta_ci(raw_stat))}

@@

d_check_nas |> select(-sub_rep, -subfield) |> filter(across(everything(), ~!is.na(.))) |> nrow()

@@

d_check_nas |> select(target_lastauthor_year, status, academic_year,  target_year,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N) |> filter(across(everything(), ~!is.na(.))) |> nrow()

@@

d_check_nas |> select(target_lastauthor_year, status, academic_year, target_year,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N, predInt, p_orig) |>  filter(across(everything(), ~!is.na(.))) |> nrow()
```

```{r}
# papers where we don't have everything

d_check_nas |> filter(if_any(everything(), ~is.na(.)))

d_check_nas |> filter(across(everything(), ~!is.na(.)))

d_check_nas  |> select(target_lastauthor_year, status, academic_year, target_year,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N, predInt, p_orig) |>  filter(if_any(everything(), ~is.na(.)))
```
